%   MSc Business Analytics Dissertation
%
%   Title:     Aaa Bbbbbbb Cccccccccc
%   Author(s): Xxxxxx Xxxxxxxxx and Yyy Yyyyyyyyy
%
%   Preface
%
%   Change Control:
%   When     Who   Ver  What
%   -------  ----  ---  --------------------------------------------------------------
%   11Feb11  AB    0.1  Begun
%

\chapter*{Preface}

% Some people like to put in a little quote (Knuth in particular loves this)

\begin{quote}
\noindent\textit{Men occasionally stumble over the truth, but most of them pick themselves up and
hurry off as if nothing had happened.}

\hspace{2cm}--- Winston Churchill
\end{quote}

The basis for this practicum stemmed from our passion towards data exploration, pattern finding, and development of new solutions. Data visualization has always been of our interest. Hence, this practicum presents an interactive visualization. It is our passion to develop interactive dashboards and serves profound insights to all types of users. We could not have achieved the success of our practicum without the constant help and support from our academic supervisor Dr. Peter Keenan and business supervisor Mr. Selwyn Hearns. We faced challenges while doing the research, but doing aggressive investigation has helped us to find answers to our questions. Research of this practicum has given us an opportunity to broaden our knowledge area towards data analysis and optimization of problems.\\

Chapter \ref{C.intro} will provide an overview of the problem this practicum is going to address with brief outline of each chapter.\\

Chapter 2 will discuss the business we are working with and what are the main contributions.\\

In chapter 3 detailed review of academic contributions towards the problem areas can be found. It will explain technologies that have been used in the past and are currently in use. Comparison between traditional systems and advanced methods can be of interest for the readers.\\

Chapter 4 will describe detailed steps of the methods followed while working on this practicum such as implementation, data discovery, etc.\\

Chapter 5 will presents results of the experiments that have been performed during the whole course of the completion of this practicum.\\

Data analysis and patterns that we have found are explained in chapter 6 and chapter 7 will provide closing statements and the scope of improvements in future.\\

The whole process could not have been achieved without a supporting group. At first, our family, who have always encouraged us with love and second, our supervisors, who have been so patient and provided their guidance throughout the practicum process. Thank you our support system for constant support.


\vspace{2em}

University College Dublin \hfill Xxxxx Xxxxxxx \\
\today \hfill Yyy Yyyyyyyyy
